---
title: "hw3_jo2570"
author: "Jai Oberoi"
date: "09/10/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading in tidyverse 
```{r}
library(tidyverse)
```

Problem 1: 

Loading in Instacart data from the p8105 datasets 
```{r}
library(p8105.datasets)
data("instacart")
```

Describing the Instacart data: 

the size of the `instacart` dataset is `r nrow(instacart)` rows and `r ncol(instacart)` columns.
we can see that the average order hour of the day is `r mean(pull(instacart, order_hour_of_day)` and the median hour is `r mean(pull(instacart, order_hour_of_day)`. The average number of days since a prior order for a user/customer is `r mean(pull(instacart, days_since_prior_order))` and the median value is `r median(pull(instacart, days_since_prior_order))`. 

We can also get a breif run-down on the data by looking the results of this skim code:
```{r}
skimr::skim(instacart)
```

```{r}
instacart %>%
  count(aisle_id) %>%
  arrange(desc(n))
```

Aisles 83 and 24 have the most products ordered with a count of over 150,000



